\section{Introduction}
Handwritten digits recognition is an old and important problem of machine learning. The objective is to recognize images of isolated handwritten digits (0-9). More
specifically, the problem is equivalent to find a model, which takes image of handwritten digit as input, and output the predicted class label of the image.
Furthermore, the ideas and methods to solve this problem would be very useful in various fields of pattern recognition problems where large volumes of real-world data is used\cite{bib:Prachi}.\\

Artificial neural networks are mathematical constructs that model certain aspects of biological neurons. Neural networks consist of one or more neurons which can exhibit complex behavior due to the nature of the connections between neurons. Neural networks can serve to store memories of data. These memories mimic biological systems in several ways\cite{bib:info-theory}.
\begin{enumerate}
	\item They are associative. With associative memories, one can recall a memory through its association with other memories.
	\item They are robust in handling error. In a neural network, memories can correct for a certain amount of error and still recall the correct memory.
	\item Memories are distributed. In a neural network, each neuron plays a part in memory storage. This is opposed to traditional computing, where a memory is associated with a specific location on the storage device.
\end{enumerate}

Hopfield network is a type of neural network named for John Joseph Hopfield (an American Scientist). It is a fully connected network which contains multiple neurons, each of which is connected to the others via weights. A key feature of Hopfield network is that it converges to a local minimum. This feature creates applications in two main areas: associative memories and optimization. With associative learning, the network can be trained to remember states which can be recalled if it is given only part of the state. Within optimization problems, as the network converges to its local minimum, the neural network's objective function can be optimized for a desired solution.