\begin{thebibliography}{1}
\bibitem{bib:Prachi}
P. Solanki, M. Bhatt, \emph{Printed Gujarati Script OCR using Hopfield Neural Network}, International Journal of Computer Applications(0975-8887), 2013.

\bibitem{bib:info-theory}
David J. C. MacKay, \emph{Information Theory, Inference, and Learning Algorithms.} New York, NY: Cambridge University Press, 2003.

\bibitem{bib:Pradeepta}
P. K. Sarangi, A. K. Sahoo, P. Ahmed, \emph{Recognition of Isolated Handwritten Oriya Numerals using Hopfield Neural Network}, International Journal of Computer Applications(0975-8887), 2012.

\bibitem{bib:Vieira}
V.M. Vieira, M. L. Lyra, C. R. da Silva, \emph{Recognition ability of the fully connected Hopfield neural network under a persistent stimulus field}, Physica A 388 (2009) 1279-1288, 2008.

\bibitem{bib:statics}
Alan Julian Izenman, \emph{Modern Multi-variate Statistical Techniques:Regression, Classification, and Manifold Learning.}, New York, NY: Springer, 2008.

\bibitem{bib:dataset}
Massimo Buscema, \emph{Semeion Handwritten Digit Data Set}, Irvine, CA: UCI Machine Learning Repository [http://www.ics.uci.edu/ mlearn/MLRepository.html], 2003.

\end{thebibliography}
\newpage
\huge \textbf{Appendix}\\

\normalsize Source code of this project could be downloaded from following link:\\

\underline{https://github.com/turbofsi/ece1512-HNN} \\

The platform of this project is on Matlab. To run this program properly, \textit{Semeion Handwritten Digit Data Set} should be downloaded beforehand and put it at same directory with all the other source code files. ex1.m is corresponding with experiment 1, and ex2.m is source code of experiment 2. 
